Model LF

### 2022-09-27 Estimation.Rmd
ændringer

```{r, message=FALSE}
AAMK <- read_excel("AAMK.xlsx")
globaldemand1 <- read_excel("globaldemand1.xlsx")

@@

```{r}
d_2006q1=create_dummy_ts(start_basic = c(2005, 2), end_basic=c(2020,1),
 dummy_start=c(2006,1), dummy_end = c(2006,1),
 basic_value = 0, dummy_value = 1, frequency = 4)

@@

 wage_ds_vars_1 <- str_c("L(TSDELTA(wage_ds), 1:4)", c(1,3,4))
 ur_ds_vars_1 <- str_c("L(TSDELTA(ur), 0:4)", c(0,2,3,4))
 prodk_ds_vars_1 <- str_c("L(TSDELTALOG(prod_ds), 0:4)", c(1,2,3,4))
 mean_dp_regul_vars_1 <- str_c("L(TSDELTALOG(mean_dp_regul), 0:4)", c(0,1,3,4))

@@

vars_out_1 <- c( mean_dp_regul_vars_1, wage_ds_vars_1,ur_ds_vars_1,prodk_ds_vars_1 )
vars_out_1

@@

>>>>

```{r, message=FALSE}
AAMK <- read_excel("AAMK.xlsx")
globaldemand1 <- read_excel("globaldemand1.xlsx")
komp_r <- read_excel("komp_r.xlsx")

@@

d_2013q1=create_dummy_ts(start_basic = c(2005, 2), end_basic=c(2020,1),
 dummy_start=c(2013,1), dummy_end = c(2013,1),
 basic_value = 0, dummy_value = 1, frequency = 4)

d_2006q1=create_dummy_ts(start_basic = c(2005, 2), end_basic=c(2020,1),
 dummy_start=c(2006,1), dummy_end = c(2006,1),
 basic_value = 0, dummy_value = 1, frequency = 4)

@@

 wage_ds_vars_1 <- str_c("L(TSDELTA(wage_ds), 1:4)", c(1,3,4))
 ur_ds_vars_1 <- str_c("L(TSDELTA(ur), 0:4)", c(0,2,3,4))
 prodk_ds_vars_1 <- str_c("L(TSDELTALOG(prod_ds), 0:4)", c(1,2,3,4))

@@

vars_out_1 <- c( wage_ds_vars_1,ur_ds_vars_1,prodk_ds_vars_1 )
vars_out_1

@@

### kuld

**Error correction model**

```{r}
reg_kuld_start=dynlm(TSDELTALOG(kuld_2017) ~ 1 + L(TSDELTALOG(kuld_2017),1:4) +  L(TSDELTALOG(komp_r_obs_2017),0:4)+ L(log(kuld_2017),1) + L(log(komp_r_obs),1)+ d_2013q1+ d_2009q1)

summary(reg_kuld_start)
```

```{r}
res_reg_kuld=residuals(reg_kuld_start)
shapiro.test(res_reg_kuld)
```

 kuld_vars_1 <- str_c("L(TSDELTALOG(kuld_2017), 1:4)", c(1,2,3,4))
 komp_r_vars_1 <- str_c("L(TSDELTALOG(komp_r_obs_2017), 0:4)", c(1,2,3))

vars_out_1 <- c( kuld_vars_1,komp_r_vars_1 )
vars_out_1

linearHypothesis(reg_kuld_start, vars_out_1, rep(0, length(vars_out_1)))

```{r}
reg_kuld=dynlm(TSDELTALOG(kuld_2017) ~ 0  +  L(TSDELTALOG(komp_r_obs_2017),c(0,4))+ L(log(kuld_2017),1) + L(log(komp_r_obs),1)+ d_2013q1+ d_2009q1)

summary(reg_kuld)
```

**quarterly data**

We only use kuld up till 2017 as the data is just fixed untill.

```{r}
kuld_2017= window(kuld, start= c(2005,1), end= c(2016,4))
komp_r_obs_2017= window(komp_r_obs, start= c(2005,1), end= c(2016,4))

reg_kuld= lm(kuld_2017 ~ komp_r_obs_2017)
summary(reg_kuld)
```
**Yearly data**

Creating the variables as yearly data:

```{r}
kuld
btyd= ts(komp_r$btyd, start = c(2005,1), end = c(2018,1), frequency = 1)
kuld= ts(komp_r$kuld, start = c(2005,1), end = c(2018,1), frequency = 1)

reg_kuld= lm(kuld ~ btyd)
summary(reg_kuld)
```

### 2022-09-27 max_dp endogen stød.Rmd
opdateret
commit
ændringer

#### Shock variables 
shock_wage_ds_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_max_dp_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_g_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_reg_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_part_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_1_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_2_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_3_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

@@

plot(komp_r_obs)
```

@@

@@

COMMENT> tilføjet
IDENTITY> nben_h_un
EQ>  nben_h_un = dp_person*unemp*kuld

@@

@@

  stat_reg = TIMESERIES(c(stat_reg),   
                       START=c(2006,1),FREQ=4),
  stat_tilpas = TIMESERIES(c(stat_tilpas),   
                       START=c(2006,1),FREQ=4),
  tilpas_pr = TIMESERIES(c(tilpas_pr),   
                       START=c(2006,1),FREQ=4),

  ## Price adjustments
  pg_adj = TIMESERIES(c(pg_adj),   
                       START=c(2005,2),FREQ=4),
  p_bd_adj = TIMESERIES(c(p_bd_adj),   
                       START=c(2005,2),FREQ=4),
  p_equip_adj = TIMESERIES(c(p_equip_adj),   
                     START=c(2005,2),FREQ=4),
  px_adj = TIMESERIES(c(px_adj),   
                        START=c(2005,2),FREQ=4),
  ## Households

@@

  yd_hk = TIMESERIES(c(yd_hk),   
                     START=c(2005,2),FREQ=4),
  nsben_h = TIMESERIES(c(nsben_h),   
                       START=c(2005,2),FREQ=4),

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4)
)
```

@@

#S_modelData$sens1 = sens1

@@

@@

wage_gap1_00 = S_model$simulation$wage_gap1
```

@@

@@

wage_gap1_01 = Shock_1$simulation$wage_gap1
```

@@

@@

plot(wage_gap_01, col= "red", ylim= c(0,1)); lines(wage_gap1_01, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

## Scenario 3 inflation

@@

```{r}
shock_1_model_shock=shock_1_model %>% window(start= c(2014,2))
```

@@

  shock_part_model = TIMESERIES(shock_part_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_max_dp_model = TIMESERIES(shock_max_dp_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_1_model = TIMESERIES(shock_1_model_shock+1 ,START=c(2014,2),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

@@

plot(komp_r_03, col= "red"); lines(komp_r_02, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(yk_ds_03, col= "red", main= "Yk_ds"); lines(yk_ds_02, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

@@

```{r}
plot((yk_ds_02 / yk_ds_00), ylim= c(0.95,1.03), col= "red");
lines((yk_ds_01w / yk_ds_00), col= "blue");
lines((yk_ds_01 / yk_ds_00), col= "green");
lines((yk_ds_03 / yk_ds_00), col= "orange")
legend("top", legend=c(""),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```

>>>>

#### Shock variables 
shock_wage_ds_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_max_dp_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_g_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_reg_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_part_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_1_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_2_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_3_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_kuld_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

@@

@@

COMMENT> 
BEHAVIORAL> shock_kuld
TSRANGE 2006 3 2016 4
EQ> TSDELTALOG(shock_kuld) =  a_2 * TSDELTALOG(TSLAG(komp_r,0))+ a_3 * TSDELTALOG(TSLAG(komp_r,4)) + a_4* log(TSLAG(komp_r,1))+ a_5* log(TSLAG(shock_kuld,1)) + a_6*d_2013q1 + a_7*d_2009q1
COEFF> a_2 a_3 a_4 a_5 a_6 a_7
STORE> coe(17)

@@

COMMENT> tilføjet
IDENTITY> nben_h_un
EQ>  nben_h_un = dp_person*unemp*kuld
IF>  shock_kuld_model <= 0
IDENTITY> nben_h_un
EQ>  nben_h_un = dp_person*unemp*shock_kuld
IF>  shock_kuld_model > 0

@@

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_kuld_model
EQ> shock_kuld_model = shock_kuld_model*1

@@

  stat_reg = TIMESERIES(c(stat_reg),   
                       START=c(2006,1),FREQ=4),
  stat_tilpas = TIMESERIES(c(stat_tilpas),   
                       START=c(2006,1),FREQ=4),
  tilpas_pr = TIMESERIES(c(tilpas_pr),   
                       START=c(2006,1),FREQ=4),
  kuld_shock = TIMESERIES(c(kuld),   
                       START=c(2005,2),FREQ=4),
  ## Price adjustments
  pg_adj = TIMESERIES(c(pg_adj),   
                       START=c(2005,2),FREQ=4),
  p_bd_adj = TIMESERIES(c(p_bd_adj),   
                       START=c(2005,2),FREQ=4),
  p_equip_adj = TIMESERIES(c(p_equip_adj),   
                     START=c(2005,2),FREQ=4),
  px_adj = TIMESERIES(c(px_adj),   
                        START=c(2005,2),FREQ=4),
  ## Households

@@

  yd_hk = TIMESERIES(c(yd_hk),   
                     START=c(2005,2),FREQ=4),

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4)
)
```

@@

#S_modelData$shock_kuld_model = shock_kuld_model

@@

kuld_00 = S_model$simulation$kuld

shock_kuld_00 = S_model$simulation$shock_kuld

@@

mk_ds_00 = S_model$simulation$mk_ds
```

@@

plot(shock_kuld_00, col= "green"); lines(kuld, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

@@

wage_gap1_01 = Shock_1$simulation$wage_gap1

shock_kuld_01 = Shock_1$simulation$shock_kuld

nben_h_un_01 = Shock_1$simulation$nben_h_un

dp_person_01 = Shock_1$simulation$dp_person

unemp_01 = Shock_1$simulation$unemp

nl_g_01 = Shock_1$simulation$nl_g
```

@@

plot(yk_ds_03, col= "red"); lines(yk_ds_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(shock_kuld_01, col= "red"); lines(shock_kuld_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

plot(emp_03, col= "red"); lines(emp_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(nl_g_01, col= "red"); lines(nl_g_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

## Scenario 3 kuld

@@

```{r}
shock_kuld_model_shock=shock_kuld_model %>% window(start= c(2006,3))
```

@@

  shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_max_dp_model = TIMESERIES(shock_max_dp_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

nben_h_un_03 = Shock_3$simulation$nben_h_un

nl_g_03 = Shock_3$simulation$nl_g

nsben_h_03 = Shock_3$simulation$nsben_h

@@

plot(komp_r_03, col= "red"); lines(komp_r_01, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(nben_h_un_01, col= "red"); lines(nben_h_un_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(yk_ds_03, col= "red", main= "Yk_ds"); lines(yk_ds_01, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

plot(nsben_h_03, col= "red"); lines(nsben_h_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

```{r}
plot(max_dp_01, col= "red"); lines(max_dp_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(dp_person_01, col= "red"); lines(dp_person_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(nben_h_un_01, col= "red"); lines(nben_h_un_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

```{r}
nben_h_un_01-nben_h_un_00
```

@@

```{r}
plot((pconk_ds_03 / pconk_ds_00), col= "red");
lines((yk_ds_01w / yk_ds_00), col= "blue");
lines((yk_ds_01 / yk_ds_00), col= "green");
lines((yk_ds_03 / yk_ds_00), col= "orange")
legend("top", legend=c(""),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```
